Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy

### 2018-08-08 draft/draft.tex
str modified

\subsection{Atomic potential}
The interaction of particle in the material is determined by interatomic potential. Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \cite{}. The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}. We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
\begin{equation} \label{eq:eam} 
	E= \displaystyle\sum
\end{equation}
\subsection{Analysis method}
\paragraph{CSP}
In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \cite{} is used to identify the nucleation and propagation of dislocations. The said centrosymmetry parameter is defined as follow:

@@

\subsection{Decrease of Strength}

The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material. Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.
1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface. This may significantly reduce the Schmid factor and thus impede slip transfer. At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree. Reorientation of slip is always required at the $\alpha_{2} / \gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree ref{}.

@@

\section{Results and Discussion}
\subsection{The influence of void on strength of TiAl alloy}

>>>>

\subsection{Atomic potential}
The interaction of particle in the material is determined by interatomic potential. Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \cite{}. The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}. We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.

\begin{equation} \label{eq:eam} 
	E= \displaystyle\sum
\end{equation}

\subsection{Analysis method}
\paragraph{CSP}
In view of the fact that dislocations cannot be easily spotted in a three-dimensional crystal, a centrosymmetry parameter \cite{} is used to identify the nucleation and propagation of dislocations. The said centrosymmetry parameter is defined as follow:

@@

\section{Results and Discussion}
%\subsection{The influence of void on strength of TiAl alloy}
\subsection{Decrease of Strength}

The existence of void detract the strength, and the void inside $\alpha$ phase grain have most significant  impact on the strength, however the void on the grain boundary have little impact on incipient strength of the material. Detailed observation of specimen with void inside the grain is shown in Figure \cite{}.
1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface. This may significantly reduce the Schmid factor and thus impede slip transfer. At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree. Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.

@@
